Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-16 paper.tex
Reword sentence a bit

In this study it was demonstrated that the performance of a high solidity
($c/R=0.28$) cross-flow turbine becomes essentially $Re$-independent at a
Reynolds number based on turbine diameter of $Re_D \approx 10^6$, or an
approximate Reynolds number based on blade chord of $Re_c \approx 2 \times
10^5$. The left side of the $C_P$--$\lambda$ curve is further diminished at low
$Re$ due to deeper stalling. The $Re$-independent threshold corresponds to that
at which the foil suction surface boundary layer becomes turbulent before having
to recover static pressure against the adverse pressure gradient, highlighted in
\cite{Lissaman1983, McMasters1980, Carmichael1981}.

>>>>

In this study it was demonstrated that the performance of a high solidity
($c/R=0.28$) cross-flow turbine becomes essentially $Re$-independent at a
Reynolds number based on turbine diameter of $Re_D \approx 10^6$, or an
approximate Reynolds number based on blade chord of $Re_c \approx 2 \times
10^5$. The power coefficient values on the left side of the $C_P$--$\lambda$
curve are further reduced at low $Re$ due to deeper stalling. The
$Re$-independent threshold corresponds to that at which the foil suction surface
boundary layer becomes turbulent before having to recover static pressure
against the adverse pressure gradient, highlighted in \cite{Lissaman1983,
    McMasters1980, Carmichael1981}.
